### 2020-10-17 readme.Rmd
clean up readme

The approach uses quasi-random sampling to generate a quadrature
scheme based (e.g Berman & Turner 1992; Foster et al, 2017). Quasi-random 
sampling quadrature are form of spatially-balanced survey design or 
point stratification, that aims to reduce the frequency of placing samples 
close to each other (relative to pseudo-random or grid designs). A 
quasi-random quadrature design improves efficiency of background point 
sampling (and subsequent modelling) by reducing the amount of spatial 
auto-correlation between data implying that each sample is providing as much 
unique information as possible (Grafston & Tille, 2013) and thus reducing low 
errors for geostatistical prediction (Diggle & Ribeiro, 2007).
The weights each quasi-random point in the quadrature scheme is calculated 
using a dirichlet tesselation (Turner 2020). To improve comptational efficiency 
\link[deldir]{deldir} funcion for a large number of of quadrature points, we 
set up an approach which breaks up the problem into manageable sub-windows. 
We do this by keeping each deldir call to less that 5000 points (which appears 
to be the point where the algorithm slowes noticibly). To avoid edge effect 
(large areas on the edges of sub-areas), we rotate the subregions three times, 
the first two use a set of prime number to closest to total number of points 
(presences+quadrature points) divided by 5000. This allows us to split the study
region in to an subsetable number of subwindows. We then take the median weight 
across all weight calculated for each point.

@@

@@

>>>>

The approach uses quasi-random sampling to generate a quadrature
scheme based (e.g Berman & Turner 1992; Foster et al, 2018). Quasi-random 
sampling quadrature are form of spatially-balanced survey design or 
point stratification, that aims to reduce the frequency of placing samples 
close to each other (relative to pseudo-random or grid designs). A 
quasi-random quadrature design improves efficiency of background point 
sampling (and subsequent modelling) by reducing the amount of spatial 
auto-correlation between data implying that each sample is providing as much 
unique information as possible (Grafston & Tille, 2013) and thus reducing low 
errors for geostatistical prediction (Diggle & Ribeiro, 2007).
The weights each quasi-random point in the quadrature scheme is calculated 
using a dirichlet tesselation (Turner 2020). To improve comptational efficiency 
\link[deldir]{deldir} funcion for a large number of of quadrature points, we 
set up an approach which breaks up the problem into manageable sub-windows. 
We do this by keeping each deldir call to less that 5000 points (which appears 
to be the point where the algorithm slowes noticibly). To avoid edge effect 
(large areas on the edges of sub-areas), we rotate the subregions three times, 
the first two use a set of prime number to closest to total number of points 
(presences+quadrature points) divided by 5000. This allows us to split the study
region in to an subsetable number of subwindows. We then take the median weight 
across all weight calculated for each point.

@@

Foster, S.D., Monk, J., Lawrence, E., Hayes, K.R., Hosack, G.R. and Przeslawski, R., 2018. Statistical Considerations for Monitoring and Sampling.

@@

Turner, Rolf, "Package ‘deldir’." (2020).
